On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-13 2_bg.tex
started making changes!

>>>>

\textcolor{red}{
This paper is based on a preliminary version published at 
SIGIR2015~\cite{ME-SIGIR15}, but adds: RQ2; 
related background on crowd sourcing;
more information on the score distributions in Section~\ref{sec:descr-stat}, including
Figures~\ref{fig:ME-raw-scores} and~\ref{fig:ME-norm-scores} and their discussion;
a new Section~\ref{sec:cs} including Figure~\ref{fig:judgeVariability} and 
recomputation of Figure~\ref{fig:workersQuality};
new material in of Section~\ref{sec:rq2}, including recomputation of 
Figures~\ref{fig:runs-rerank-median3best} and~\ref{fig:runs-rerank-median3best-fake}; 
a revised second half of Section~\ref{sec-rq3}; 
an Appendix giving exact participant instructions; and
additional references.
}

### 2016-09-13 4_descriptive_stats.tex
started making changes!

%\myparagraph{Crowd Judging:}
As detailed in Table~\ref{tab:descr-stat}, with 7,059 units comprised
of 8 documents each, we collected more than 50,000 judgments in total,
at a cost of around $\$1,700$ (CrowdFlower fees included).
This is in the order of magnitude of $\$0.4$ for each document, which
is broadly competitive when compared with the cost of TREC assessors
or other similar crowdsourcing initiatives; for example, according to
\citet[Footnote~2]{Alonso:2012}, gathering ordinal scale judgments
cost around $\$0.1$ per document.
However, the comparison is more favorable when considering that in our
experiments 10 redundant judgments per document are collected, and the
\nkn and \hkh documents receive multiple judgments, whereas in Alonso
and Mizzaro's work only 5 redundant judgments were collected, and
there was nothing similar to our \nkn vs. 
\hkh check.
We return to the cost issues in more detail in 
Section~\ref{sec:how-many-workers}, where the number of repeat
judgments that are required for stable ME estimates is investigated.

>>>>

%\myparagraph{Crowd Judging:}
As detailed in Table~\ref{tab:descr-stat}, with 7,059 units each of
8 documents, we collected more than 50,000 judgments in total,
at a cost of around $\$1,700$ (CrowdFlower fees included).
This is in the order of magnitude of $\$0.4$ for each document, which
is broadly competitive when compared with the cost of TREC assessors
or other similar crowdsourcing initiatives; for example, according to
\citet[Footnote~2]{Alonso:2012}, gathering ordinal scale judgments
cost around $\$0.1$ per document.
However, the comparison is more favorable when considering that in our
experiments 10 redundant judgments per document are collected, and the
\nkn and \hkh documents receive multiple judgments, whereas in Alonso
and Mizzaro's work only 5 redundant judgments were collected, and
there was nothing similar to our \nkn vs. 
\hkh check.
We return to the cost issues in more detail in 
Section~\ref{sec:how-many-workers}, where the number of repeat
judgments that are required for stable ME estimates is investigated.
